Neural Neural Textures Make Better Simulators ``I Can't Believe It's Not Real!''

### 2022-06-14 CORL/example.tex
Group Meeting June 13

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=200pt]{../images/module_translator.pdf}
		\end{center}
		\caption{
			A subset of figure \ref{fig:main_diagram} focusing on the image translation module $T$.
		}
		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
		\label{fig:module_translator}
	\end{figure}

@@

	To keep the object surfaces consistent between a batch of $N$ outputs, we impose a pixel-wise ``unprojection consistency loss'' between these surfaces by unprojecting them back into a common texture space.
	\begin{equation}
		u\toNL=\text{unproject}(\ph\toN,s\toN)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_N
	\end{equation}

@@

	This loss is a fairly intuitive and effective way to maintain surface consistency. There are some caveats, however.
	In order to produce a standard deviation greater than $0$, we must have a batch size greater than $1$.
	Furthermore, environments that rarely show a particular region of a surface will rarely have $\lUC$ applied to that region because they're unlikely to show up twice in the same batch.
	For this reason, $\lUC$ is most useful with large batch sizes.% because observing the same surface in multiple elements of a batch becomes more likely as the batch size increases. 
	But because video memory limits our batch sizes, first-person environments might be more of a challenge for $\lUC$ - particularly when exploring multiple rooms (a task we haven't done though - should I mention this?)

>>>>

% 	\begin{figure}[H]
% 		\begin{center}
% 			\includegraphics[width=200pt]{../images/module_translator.pdf}
% 		\end{center}
% 		\caption{
% 			A subset of figure \ref{fig:main_diagram} focusing on the image translation module $T$.
% 		}
% 		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
% 		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
% 		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
% 		\label{fig:module_translator}
% 	\end{figure}

@@

	To keep the object surfaces consistent between a batch of $N$ outputs, we impose a pixel-wise ``unprojection consistency loss'' between these surfaces by unprojecting them back into a common texture space.
	\begin{equation}
		u\toNL=\text{unproject}(\ph\toN,s\toN)\ \ \ \text{ and } \ \ \ \lUC \Rightarrow u_1 \approx u_2 \dots \approx u_N
	\end{equation}

@@

%MOVE THIS TO APPENDIX
% 	This loss is a fairly intuitive and effective way to maintain surface consistency. There are some caveats, howe/ver.
% 	In order to produce a standard deviation greater than $0$, we must have a batch size greater than $1$.
% 	Furthermore, environments that rarely show a particular region of a surface will rarely have $\lUC$ applied to that region because they're unlikely to show up twice in the same batch.
% 	For this reason, $\lUC$ is most useful with large batch sizes.% because observing the same surface in multiple elements of a batch becomes more likely as the batch size increases. 
% 	But because video memory limits our batch sizes, first-person environments might be more of a challenge for $\lUC$ - particularly when exploring multiple rooms (a task we haven't done though - should I mention this?)
